Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-05-01 paper/structureScene.tex
non-linear --> nonlinear

Scattering transforms are time-shift invariant representations of audio signals computed by applying auditory and modulation filter banks alternated with complex modulus non-linearities.
This section first explains the importance of local invariance to time-shifting and stability to time-warping in the representation of acoustic scenes, then describes how the scattering transform is designed to satisfy these properties while having a high discriminative power.

@@

Finally, the SVM can also be extended to handle non-linear decision surfaces. This is obtained using the ``kernel trick'', which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A non-linear mapping then results in a non-linear decision surface in the orignal space.

>>>>

Scattering transforms are time-shift invariant representations of audio signals computed by applying auditory and modulation filter banks alternated with complex modulus nonlinearities.
This section first explains the importance of local invariance to time-shifting and stability to time-warping in the representation of acoustic scenes, then describes how the scattering transform is designed to satisfy these properties while having a high discriminative power.

@@

Finally, the SVM can also be extended to handle nonlinear decision surfaces. This is obtained using the ``kernel trick'', which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A nonlinear mapping then results in a nonlinear decision surface in the orignal space.
